Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-02-10 MCQMC2022ChallengesQMCSoftwareArticle.tex
Updates from Overleaf

An \emph{LD generator}, such as a lattice, digital net, or Halton point generator supplies the sequence $\bsx_1, \bsx_2, \ldots$.  These sequences may be deterministic or random and are intended to have an empirical distribution that approximates well the uniform distribution.

@@

The most prevalent generally available QMC software are LD generators. They appear in ACM publications \cite{BraFox88,BraFoxNie92,HonHic00a}, FinDer \cite{PasTra95,FinDer}, BRODA \cite{BRODA20a}, NAG \cite{NAG27}, and MATLAB \cite{MAT9.13}.

>>>>

An \emph{LD generator}, such as a lattice, digital net, or Halton point generator supplies the sequence $\bsx_1, \bsx_2, \ldots$.  These sequences may be deterministic or random and are intended to have an empirical distribution that approximates well the uniform distribution.  LD generators are the most prevalent generally available components of QMC software.  These generators appear in Association of Computing Machinery  publications \cite{BraFox88,BraFoxNie92,HonHic00a}, FinDer \cite{PasTra95,FinDer}, BRODA \cite{BRODA20a}, NAG \cite{NAG27}, and MATLAB \cite{MAT9.13}.

@@
